\section{Commissioning Data Releases} \label{sect:commissioning}

Distributing commissioning data to the LSST data rights community brings the mutual benefits
of preparing the community for LSST data and giving the LSST team the opportunity to prepare
for efficient operations. This policy balancing
early science with the importance of ensuring fair access to LSST data for LSST Data Rights
holders is still being decided but we outline a likely scenario here.

\subsection{Commissioning Interface} \label{sect:cominterface}

LSST will make a best effort to distribute commissioning data through an early version of the
Science User Interface that the community will use to access LSST data during 10-year survey
operations. However, before full operations, the LSST’s Science Platform and suite of user
services will be operating at limited capacity and with limited functionality.
{\bf TBD - this is actually tricky with authentication}
The minimum data
products to be made available would be through flat files (e.g. FITS images and tables), the
desired distribution would be through a still emerging DAC (i.e. without full services), and with
provisional access to file systems and databases.

Some user groups will be interested in the bulk transfer of commissioning data from the LSST
DAC at NCSA to their own facility. The technical details and possible cost of such bulk data
distribution is TBD. This cost will be supported by the user groups, and not by LSST.

\subsection{Alerts} \label{sect:alerts}
Early alert stream data will also be distributed, possibly with substantial latency, to
familiarize the community with the planned format and content of the alert stream.
At best-effort alert stream may be distributed around August 2021.

\subsubsection{Distribution Mechanism}
Kafka/AVRO based system currently being tested on ZTF.

\subsection{ComCam Release - end 2020}
Currently ComCam ends  around August 2020 - allowing a few months for cleaning and documenting the
ComCam Images and source catalogs  could be available 3-6 months later hence by end of 2020 {\bf iff} the schedule holds and ComCam finishes mid 2020.

\subsection{Commissioning Full Camera  Release - end Q3 2021} \label{sect:cfc}
Currently commissioning of the Full Camera ends  around March 2021 before the mini surveys start.
Again allowing for clean up and documenting,  Images and source catalogs  could be available 3-6 months later around September 2021.

\subsection{Mini Surveys  Release - end 2021}
The Mini-Surveys ends  around August 2021 - they commence directly as commissioning the Full Camera Ends  hence this data release may be affected by preparations of the prior release \secref{sect:cfc}.
Hence, effort permitting,  Images and source catalogs from the mini surveys may be available by end of 2021.
